Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-24 ECCV/paper.tex
Changed template to ECCV 2014

Concentric Rings\cite{concentric} \\
Multicolor rings \cite{Cho:2001} \cite{Cho97fastcolor} \\
Circular Data Matrix Fiducial System \cite{NaimarkF02} \\

>>>>

Concentric Rings\cite{NaimarkF02} \\
Multicolor rings \cite{Cho:2001} \cite{Cho97fastcolor} \\
Circular Data Matrix Fiducial System \cite{NaimarkF02} \\
